---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sherlock

<!-- badges: start -->
<!-- badges: end -->

The __{sherlock} R package__ provides powerful graphical displays and statistical tools to aid structured problem solving and diagnosis. It is designed to seamlessly work with the `tidyverse` set of packages.


_"That is to say, nature's laws are causal; they reveal themselves by comparison and difference, and they operate at every multi-variate space-time point" - Edward Tufte_





## Installation

You can install the development version of sherlock from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("gaborszabo11/sherlock")
```

## Functions

While the package is currently under development, a few functions are already available and ready to be used. Available functions are as follows:


#### Plotting functions
`draw_multi_vari_plot()`

`draw_cartesian_small_multiples()`

`draw_polar_small_multiples()`

`draw_youden_plot()`

#### Helper functions
`theme_sherlock()`

`scale_color_sherlock()`



## Examples

Here are a few examples :

```{r example}
library(sherlock)
library(ggh4x)

multi_vari_data %>% 
  draw_multi_vari_plot(response = force, factor_1 = cycle, factor_2 = fixture, factor_3 = line)
```



```{r}
library(sherlock)
library(ggh4x)

multi_vari_data_2 %>% 
  draw_multi_vari_plot(response = Length, factor_1 = Part, factor_2 = Operator, plot_means = TRUE)
```


Here's another example:


```{r}
youden_plot_data_2 %>% 
  draw_youden_plot(x_axis_var = gage_1, y_axis_var = gage_2, median_line = TRUE, 
                   x_axis_label = "Gage 1", y_axis_label = "Gage 2")
```


```{r}
youden_plot_data %>% 
  draw_youden_plot(x_axis_var = measurement_1, y_axis_var = measurement_2, 
                   grouping_var = location, x_axis_label = "Trial 1", y_axis_label = "Trial 2")
```




## References
Diagnosing Performance and Reliability, David Hartshorne and The New Science of Fixing Things, 2019

Statistical Engineering - An Algorithm for Reducing Variation in Manufacturing Processes, Stefan H. Steiner and Jock MacKay, 2005

